### 2018-11-16 Sections/cloud_quantum_computing.tex
Fixed up fig sizes for 1 col
completed CV sec
minor

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{distributed}
\captionspacefig \caption{Models for distributed computation in parallel and in series. In parallel, a root node oversees the total computation, delegating tasks to child nodes, which process data independently of one another before being merged. In series the nodes sequentially process data in a pipeline of algorithmic stages.} \label{fig:distributed}
\end{figure}

@@

This architecture is merely a direct mapping of classical \textsc{MapReduce} to the quantum setting. How might it be used? Consider quantum simulation, where we aim to simulate a Hamiltonian of the form,
\begin{align}
\hat{H}_\mathrm{total} = \sum_i \hat{H}_i,	
\end{align}
where each of the $\hat{H}_i$ terms are local Hamiltonians acting on orthogonal Hilbert spaces. This implies that all terms commute,
\begin{align}
[\hat{H}_i,\hat{H}_j]=0,
\end{align}
and therefore the unitaries they generate,
\begin{align}
	\hat{U}_j=e^{-\frac{i\hat{H}_jt}{\hbar}},
\end{align}
have a separable tensor product structure,
\begin{align}
	\hat{U}_\mathrm{total}=\bigotimes_i \hat{U}_i.
\end{align}
This separability lends itself directly to the tensor product structure of the \textsc{Execute} unitaries. The \textsc{Map} operation could now be a stage for preparing entangled initial states, and the \textsc{Reduce} operation might perform collective measurements.

@@

For example, with four nodes the 2-bit identification numbers are, 
\begin{align}
	y=\{00,01,10,11\}.
\end{align}
If the input search space is $N$-bits in length, then each of the nodes are assigned the search-space \mbox{$x'\frown y$}, where $x'$ is an \mbox{$N-2$}-bit number. Within each instance, the Grover search searches over only the reduced space $x'$, with $y$ a constant of the instance. Fig.~\ref{fig:distributed_search} illustrates the circuit schematic for this simple example.

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{modules_physical}
	\captionspacefig \caption{A possible physical realisation of commercially produced quantum modules\index{Node-X}, forming a \mbox{$2\times 3$} patchwork of cluster states. Each hosts a relatively small number of qubits. The nodes each have four optical interconnects, which are used to connect the modules via optical fibre. Entangling operations performed on photons shared via the interconnects create inter-module entanglement links, yielding a distributed virtual quantum computer with far more qubits. The computation is truly distributed and cooperative, in the sense that the entire computation is non-local, instead being collectively distributed across all the nodes, which coordinate their local operations via only classical communication. An alternate implementation is to replace the inter-node quantum links with Bell-pair distributers. Then entanglement swapping can be employed to swap the entanglement into a link between nodes.}\label{fig:modules_physical}
\end{figure}

@@

In Sec.~\ref{sec:economics} we argue that in the quantum era it will be optimal to unify the world's quantum computers into a single virtual, distributed device, rather than utilising smaller individual quantum computers in isolation. This owes to the super-linear scaling in the power of a quantum computer against its number of constituent qubits, a phenomena unique to quantum computers.

>>>>

\begin{figure}[!htbp]
\if 2\pubmode
	\includegraphics[clip=true, width=0.475\textwidth]{distributed}
\else
	\includegraphics[clip=true, width=0.6\textwidth]{distributed}
\fi
\captionspacefig \caption{Models for distributed computation in parallel and in series. In parallel, a root node oversees the total computation, delegating tasks to child nodes, which process data independently of one another before being merged. In series the nodes sequentially process data in a pipeline of algorithmic stages.} \label{fig:distributed}
\end{figure}

@@

This architecture is merely a direct mapping of classical \textsc{MapReduce} to the quantum setting. How might it be used? Consider quantum simulation\index{Quantum simulation}, where we aim to simulate a Hamiltonian of the form,
\begin{align}
\hat{H}_\mathrm{total} = \sum_i \hat{H}_i,	
\end{align}
where each of the $\hat{H}_i$ terms are local Hamiltonians acting on orthogonal Hilbert spaces. This implies that all terms commute,
\begin{align}
[\hat{H}_i,\hat{H}_j]=0,
\end{align}
and therefore the unitaries they generate,
\begin{align}
	\hat{U}_j=e^{-\frac{i\hat{H}_jt}{\hbar}},
\end{align}
have a separable tensor product structure,
\begin{align}
	\hat{U}_\mathrm{total}=\bigotimes_i \hat{U}_i.
\end{align}
This separability lends itself directly to the tensor product structure of the \textsc{Execute} unitaries. The \textsc{Map} operation could now be a stage for preparing entangled initial states (entangled across the different subsystems), and the \textsc{Reduce} operation might perform collective measurements or sampling.

@@

For example, with four nodes the 2-bit identification numbers are, 
\begin{align}
	y=\{00,01,10,11\}.
\end{align}
If the input search space is $N$-bits in length, then each of the nodes are assigned the search-space \mbox{$x'\frown y$}, where $x'$ is an \mbox{$N-2$}-bit number. Within each instance, the Grover search searches over only the reduced space $x'$, with $y$ a constant of the instance. Fig.~\ref{fig:distributed_search} illustrates the circuit schematic for the simple \mbox{$M=4$} example.

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{modules_physical}
	\captionspacefig \caption{A possible physical realisation of commercially produced quantum modules\index{Node-X}, forming a \mbox{$2\times 3$} patchwork of cluster states. Each hosts a relatively small number of qubits. The nodes each have four optical interconnects, which are used to connect the modules via optical fibre. Entangling operations performed on photons shared via the interconnects create inter-module entanglement links, yielding a distributed virtual quantum computer with far more qubits. The computation is truly distributed and cooperative, in the sense that the entire computation is non-local, instead being collectively distributed across all the nodes, which coordinate their local operations via only classical communication. An alternate implementation is to replace the inter-node quantum links with Bell pair distributers. Then entanglement swapping can be employed to swap the entanglement into a link between nodes.}\label{fig:modules_physical}
\end{figure}

@@

In Sec.~\ref{sec:economics} we argue that in the quantum era it will be optimal to unify the world's quantum computers into a single virtual, distributed device, rather than utilising smaller individual quantum computers in isolation. This owes to the super-linear scaling in the power of a quantum computer against its number of constituent qubits, a phenomena unique to quantum computers with no classical parallel.

### 2018-11-16 Sections/cryptowars.tex
minor

Hacking attacks in this context exploit weaknesses in the physical implementation, rather than weakness of the theory -- so-called `side-channel attacks'\index{Side-channel attacks}. Some examples of weaknesses which allow zero-error attacks\index{Zero-error attacks} include losses, imperfect components, or correlations between signals leaking information from the system.

When considering the security of noisy channels, one must assume that all noise is due to manipulation by an eavesdropper, the worst-case scenario. An attempted attack is considered successful if it can be proven that the eavesdropper can gain a non-negligible (i.e not exponentially small) amount of mutual information with the final secret-key established between Alice and Bob, without alerting them. Some of the best-known attacks follow:

>>>>

Hacking attacks in this context exploit weaknesses in the physical implementation, rather than weakness of the theory -- so-called `side-channel attacks'\index{Side-channel attacks}. Some examples of weaknesses which allow zero-error attacks\index{Zero-error attacks} include:

\begin{itemize}
	\item Losses: Genuinely lossy channels or components are indistinguishable from ideal ones where some of the signal has been tapped off by Eve. Therefore, we must always assume the worst, that whatever is lost from our system is in the hands of Eve.
	\item Imperfect components: Our physical implementation might just not be operating strictly according to the theory.
	\item Correlations: Mutual information between signals in our system may leak information from the secure system to the environment, where Eve might be waiting patiently.
\end{itemize}

When considering the security of noisy channels, one must assume that all noise is due to manipulation by an eavesdropper -- the worst-case scenario. An attempted attack is considered successful if it can be proven that the eavesdropper can gain a non-negligible (i.e not exponentially small) amount of mutual information with the final secret-key established between Alice and Bob, without alerting them. Some of the best-known attacks follow:

### 2018-11-16 Sections/economics_of_the_quantum_internet.tex
minor

From a policy implications perspective, this means that governments wanting to cash in on the new technology need to be cautious with the imposition of taxes relative to market maturity \comment{What does this mean?}. Imposing a significant tax early on may only act as a disincentive to the development of the industry. However, once the market matures further, the imposition of a qubit tax would make strong economic sense, as there will be minimal loss of market efficiency. Importantly, such a tax on computational power alone could serve to be a relatively stable revenue generation tool for governments.

>>>>

From a policy implications perspective, this means that governments wanting to cash in on the new technology need to be cautious with the imposition of taxes relative to market maturity. Imposing a significant tax early on may only act as a disincentive to the development of the industry. However, once the market matures further, the imposition of a qubit tax would make strong economic sense, as there will be minimal loss of market efficiency. Importantly, such a tax on computational power alone could serve to be a relatively stable revenue generation tool for governments.

### 2018-11-16 Sections/physical_architectures_for_quantum_computing.tex
minor

However, although this procedure works in-principle, it comes at the expense of a large number of sources, $N$, and more challengingly, fast-feedforward. Keep in mind that if we were able to perform complex fast-feedforward, we might be able to do much more (and far more interesting things) than just \textsc{BosonSampling} in the first place!

@@

% \comment{Is this right?}

% \comment{Can we distinguish all 4 Bell states, or just 2 like LOQC?}

>>>>

However, although this procedure works in-principle, it comes at the expense of a large number of sources, $N$, and more challengingly, fast-feedforward. Keep in mind that if we were able to perform complex fast-feedforward, we might be able to do much more (and far more interesting things) than just \textsc{BosonSampling} in the first place (i.e universal LOQC)!

@@

\comment{Is the Bell projection deterministic, and, can it distinguish all four?}

### 2018-11-16 Sections/protocols_for_the_quantum_internet.tex
minor

\subsection{More exotic states of light}

As discussed in Sec.~\ref{sec:exotic}, many other far more elaborate states are very difficult to prepare, and it would be highly desirable if they could be obtained/purchased over a quantum network. This includes certain CV states, which have utility in alternate models for quantum computing \cite{bib:Menicucci06, Ralph, Lund}.

\comment{To do!}

\comment{Add hyperlinks to other relevant sections}

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{LO_archs_long}
	\captionspacefig \caption{The three primary approaches for implementing linear optics transformations. (a) Bulk optics\index{Bulk optics}, where each optical mode is spatially encoded, and the linear transformation is decomposed into a discrete array of beamsplitters and phase-shifters, an appropriate choice of which enables arbitrary linear optics transformations to be implemented. (b) Time-bin encoding\index{Time-bin encoding}\index{Fibre-loops}, where each optical mode is designated a distinct time-bin. Fibre-loops meeting at dynamically reconfigurable beamsplitters enable arbitrary linear transformations to be implemented. (c) Integrated wave-guide chips\index{Waveguides}, where evanescent coupling between neighbouring wave-guides within a chip facilitates interference between modes (graphic courtesy of Alberto Peruzzo \cite{bib:PeruzzoQW}). (d) Integrated wave-guide chip with electrically controllable phase-shifters, implementing a programmable, universal \mbox{$6\times 6$} linear optics network (graphic courtesy of Jeremy O'Brien \cite{bib:carolan2015universal}\comment{Get permission}).} \label{fig:LO_archs}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=\textwidth]{LO_archs}
	\captionspacefig \caption{The three primary approaches for implementing linear optics transformations. (a) Bulk optics\index{Bulk optics}, where each optical mode is spatially encoded, and the linear transformation is decomposed into a discrete array of beamsplitters and phase-shifters, an appropriate choice of which enables arbitrary linear optics transformations to be implemented. (b) Time-bin encoding\index{Time-bin encoding}\index{Fibre-loops}, where each optical mode is designated a distinct time-bin. Fibre-loops meeting at dynamically reconfigurable beamsplitters enable arbitrary linear transformations to be implemented. (c) Integrated wave-guide chips\index{Waveguides}, where evanescent coupling between neighbouring wave-guides within a chip facilitates interference between modes (graphic courtesy of Alberto Peruzzo \cite{bib:PeruzzoQW}). (d) Integrated wave-guide chip with electrically controllable phase-shifters, implementing a programmable, universal \mbox{$6\times 6$} linear optics network (graphic courtesy of Jeremy O'Brien \cite{bib:carolan2015universal}\comment{Get permission}).} \label{fig:LO_archs}
	\end{figure*}
\fi

@@

Another common non-linear transformation is squeezing, discussed in Sec.~\ref{sec:squeezed}. This implements the unitary operator\index{Squeezing operator},
\begin{align}
\hat{S}(\xi) = \exp \left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
where $\xi$ is the squeezing parameter, which has the effect of applying a dilation of some arbitrary factor in phase-space.

Thus, jointly, the displacement and squeezing operators enable arbitrary translations and dilations in phase-space. These operations form the basis for CV quantum computing schemes, to be discussed in more detail in Sec.~\ref{sec:CV_QC}.

@@

There are countless non-optical systems applicable to quantum information processing applications. For example, quantum computing schemes have been described using: two-level\index{2-level atoms} or $\lambda$-configuration atoms\index{$\lambda$-configuration systems}; superconducting rings\index{Superconductors!Rings}; ion traps\index{Ion traps}; atomic ensembles\index{Atomic ensembles}; and countless more.

\comment{Some citations}

@@

\begin{figure}[!htpb]
	\if 3\pubmode
	\includegraphics[clip=true, width=0.7\textwidth]{W_state_memory}
	\else
		\includegraphics[clip=true, width=0.475\textwidth]{W_state_memory} has  has 
	\fi
	\caption{Quantum memory based on W-state encoding. Rails represent optical modes, and the input logical qubit state, $\ket{L}$, is represented using dual-rail encoding. The QFT fanout operation maps each of the two input basis states to one of two orthogonal $N$-qubit W-states, $\ket{W}$, differing only by their phase relationships. These are then fed into a bank of $N$ quantum memories. To readout the memories we convert back to optical encoding and decode using the inverse QFT operation. Success of the protocol is defined as there being exactly one photon between the first two `success' output modes. If a photon leaks into any of the other `failure' output modes we discard the state and assume it was erroneous. Thus error detection is heralded via the presence or absence of a photon in the `failure' modes.}\label{fig:W_state_memory}
\end{figure}

>>>>

%\subsection{More exotic states of light}

%As discussed in Sec.~\ref{sec:exotic}, many other far more elaborate states are very difficult to prepare, and it would be highly desirable if they could be obtained/purchased over a quantum network. This includes certain CV states, which have utility in alternate models for quantum computing \cite{bib:Menicucci06, Ralph, Lund}.

@@

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{LO_archs_long}
	\captionspacefig \caption{The three primary approaches for implementing linear optics transformations. (a) Bulk optics\index{Bulk optics}, where each optical mode is spatially encoded, and the linear transformation is decomposed into a discrete array of beamsplitters and phase-shifters, an appropriate choice of which enables arbitrary linear optics transformations to be implemented. (b) Time-bin encoding\index{Time-bin encoding}\index{Fibre-loops}, where each optical mode is designated a distinct time-bin. Fibre-loops meeting at dynamically reconfigurable beamsplitters enable arbitrary linear transformations to be implemented. (c) Integrated wave-guide chips\index{Waveguides}, where evanescent coupling between neighbouring wave-guides within a chip facilitates interference between modes (graphic courtesy of Alberto Peruzzo \cite{bib:PeruzzoQW}). (d) Integrated wave-guide chip with electrically controllable phase-shifters, implementing a programmable, universal \mbox{$6\times 6$} linear optics network (graphic courtesy of Jeremy O'Brien \cite{bib:carolan2015universal}).} \label{fig:LO_archs}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=\textwidth]{LO_archs}
	\captionspacefig \caption{The three primary approaches for implementing linear optics transformations. (a) Bulk optics\index{Bulk optics}, where each optical mode is spatially encoded, and the linear transformation is decomposed into a discrete array of beamsplitters and phase-shifters, an appropriate choice of which enables arbitrary linear optics transformations to be implemented. (b) Time-bin encoding\index{Time-bin encoding}\index{Fibre-loops}, where each optical mode is designated a distinct time-bin. Fibre-loops meeting at dynamically reconfigurable beamsplitters enable arbitrary linear transformations to be implemented. (c) Integrated wave-guide chips\index{Waveguides}, where evanescent coupling between neighbouring wave-guides within a chip facilitates interference between modes (graphic courtesy of Alberto Peruzzo \cite{bib:PeruzzoQW}). (d) Integrated wave-guide chip with electrically controllable phase-shifters, implementing a programmable, universal \mbox{$6\times 6$} linear optics network (graphic courtesy of Jeremy O'Brien \cite{bib:carolan2015universal}).} \label{fig:LO_archs}
	\end{figure*}
\fi

@@

Another common non-linear transformation is squeezing, discussed in Sec.~\ref{sec:squeezed_prep}. This implements the unitary operator\index{Squeezing operator},
\begin{align}
\hat{S}(\xi) = \exp \left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
where $\xi$ is the squeezing parameter, which has the effect of applying a dilation of some arbitrary factor along a particular axis in phase-space.

Thus, jointly, the displacement and squeezing operators enable arbitrary translations and dilations in phase-space\index{Phase-space}. These operations form the basis for CV quantum computing schemes, to be discussed in more detail in Sec.~\ref{sec:CV_QC}.

@@

There are countless non-optical systems applicable to quantum information processing applications. For example, quantum computing schemes have been described using:
\begin{itemize}
	\item Two-level\index{2-level atoms}.
	\item $\lambda$-configuration atoms\index{$\lambda$-configuration systems}.
	\item Superconducting rings\index{Superconductors!Rings}.
	\item Ion traps\index{Ion traps}.
	\item Atomic ensembles\index{Atomic ensembles}.
	\item Countless more\ldots
\end{itemize}

@@

\begin{figure}[!htpb]
	\if 3\pubmode
	\includegraphics[clip=true, width=0.7\textwidth]{W_state_memory}
	\else
		\includegraphics[clip=true, width=0.475\textwidth]{W_state_memory} 
	\fi
	\caption{Quantum memory based on W-state encoding. Rails represent optical modes, and the input logical qubit state, $\ket{L}$, is represented using dual-rail encoding. The QFT fanout operation maps each of the two input basis states to one of two orthogonal $N$-qubit W-states, $\ket{W}$, differing only by their phase relationships. These are then fed into a bank of $N$ quantum memories. To readout the memories we convert back to optical encoding and decode using the inverse QFT operation. Success of the protocol is defined as there being exactly one photon between the first two `success' output modes. If a photon leaks into any of the other `failure' output modes we discard the state and assume it was erroneous. Thus error detection is heralded via the presence or absence of a photon in the `failure' modes.}\label{fig:W_state_memory}
\end{figure}

### 2018-11-16 Sections/quantum_algorithms.tex
minor

\comment{To do - Heliang}

@@

From the superposition state, the uniform mixture of simplices state,
\begin{align}
\hat\rho_k^\epsilon = \frac{1}{|S_k^\epsilon|} \sum_{s_k\in S_k^\epsilon} \ket{s_k}\bra{s_k},
\end{align}
is easily prepared with the addition of CNOT gates and ancillary qubits\footnote{Using parallel CNOT gates one can transform an arbitrary superposition state into a redundantly encoded equivalent, \mbox{$\hat{U}_\mathrm{CNOTs}\sum_i \lambda_i \ket{\psi_i}\ket{0} \to \sum_i \lambda_i \ket{\psi_i}\ket{\psi_i}$}, following which tracing out the redundant copy takes us to its uniform mixture, \mbox{$\sum_i |\lambda_i|^2\ket{\psi_i}\bra{\psi_i}$}.}.

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function TDA(dataPoints):
\begin{enumerate}
	\item Implement a Grover search on the set of data-points with set-membership oracle function,
	\begin{align}
f_\epsilon(s_k) = \left\{ \begin{matrix}
 1, & \mathrm{if}\,\,s_k\in S_k^\epsilon \\
 0, & \mathrm{otherwise}
\end{matrix}\right.,
\end{align}
which prepares the simplicial complex superposition state,
\begin{align}
\ket\psi_k^\epsilon = \frac{1}{\sqrt{|S_k^\epsilon|}} \sum_{s_k\in S_k^\epsilon} \ket{s_k},
\end{align}
	\item Using ancillary qubits, CNOT gates and a trace-out operation, prepare the simplicial complex uniform mixed state,
	\begin{align}
\hat\rho_k^\epsilon = \frac{1}{|S_k^\epsilon|} \sum_{s_k\in S_k^\epsilon} \ket{s_k}\bra{s_k},
\end{align}
	\item Perform quantum phase-estimation on the simplicial complex mixed state.
	\item \comment{To do - show how Betti numbers are calculated. Formulas.}
	\item Algorithm has runtime,
\begin{align}
O(n^5/\delta),
\end{align}
for accuracy $\delta$.
\item $\Box$
\end{enumerate}
\begin{center}
\if 2\pubmode
	\includegraphics[clip=true, width=\textwidth]{TDA_circuit}
\else
	\includegraphics[clip=true, width=0.6\textwidth]{TDA_circuit}
\fi
\end{center}
}
\end{mdframed}
\captionspacealg \caption{Quantum topological data analysis algorithm for calculating Betti numbers.} \label{alg:TDA}
\end{table}

\comment{Finish mathematical details}

@@

@@

If we lay out the circuit in 2D (hence the 2D HLF problem), it only requires classically-controlled Clifford gates\index{Clifford gates} between nearest neighbour qubits on a 2D grid. An example is shown in Fig.~\ref{fig:2DHLFgrid}. An instance of the HLF problem can be described by a graph $G(A)$ with $n$ vertices such that the off-diagonal part of A is the adjacency matrix of $G(A)$. Here $A_{i,j}=0$ unless $i,j$ are nearest neighbour vertices of the grid or $i = j$. We place qubits at each vertex and every edge corresponds to an input bit. The HLF problem is solved by applying nearest-neighbour $C_Z$ gates and $S_i$ phase gates at the correct site.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{shallow_circuits_2D}
\caption{\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid. The qubits are represented as green circles (some omitted for clarity), and $C_Z$ gates are drawn in red.}
\end{figure}

>>>>

@@

From the superposition state, the uniform mixture of simplices state,
\begin{align}
\hat\rho_k^\epsilon = \frac{1}{|S_k^\epsilon|} \sum_{s_k\in S_k^\epsilon} \ket{s_k}\bra{s_k},
\end{align}
is easily prepared with the addition of CNOT gates and ancillary qubits\footnote{Using parallel CNOT gates one can transform an arbitrary superposition state into a redundantly encoded equivalent, \mbox{$\hat{U}_\mathrm{CNOTs}\sum_i \lambda_i \ket{\psi_i}\ket{0} \to \sum_i \lambda_i \ket{\psi_i}\ket{\psi_i}$}, following which tracing out the redundant copy takes us to its uniform mixture, \mbox{$\hat\rho=\sum_i |\lambda_i|^2\ket{\psi_i}\bra{\psi_i}$}.}.

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function TDA(dataPoints):
\begin{enumerate}
	\item Implement a Grover search on the set of data-points with set-membership oracle function,
	\begin{align}
f_\epsilon(s_k) = \left\{ \begin{matrix}
 1, & \mathrm{if}\,\,s_k\in S_k^\epsilon \\
 0, & \mathrm{otherwise}
\end{matrix}\right.,
\end{align}
which prepares the simplicial complex superposition state,
\begin{align}
\ket\psi_k^\epsilon = \frac{1}{\sqrt{|S_k^\epsilon|}} \sum_{s_k\in S_k^\epsilon} \ket{s_k},
\end{align}
	\item Using ancillary qubits, CNOT gates and a trace-out operation, prepare the simplicial complex uniform mixed state,
	\begin{align}
\hat\rho_k^\epsilon = \frac{1}{|S_k^\epsilon|} \sum_{s_k\in S_k^\epsilon} \ket{s_k}\bra{s_k},
\end{align}
	\item Perform quantum phase-estimation on the simplicial complex mixed state.
	\item Classical post-processing reveals the Betti numbers.
	\item Algorithm has runtime,
\begin{align}
O\left(\frac{n^5}{\delta}\right),
\end{align}
for accuracy $\delta$.
\item $\Box$
\end{enumerate}
\begin{center}
\if 2\pubmode
	\includegraphics[clip=true, width=\textwidth]{TDA_circuit}
\else
	\includegraphics[clip=true, width=0.6\textwidth]{TDA_circuit}
\fi
\end{center}
}
\end{mdframed}
\captionspacealg \caption{Quantum topological data analysis algorithm for calculating Betti numbers.} \label{alg:TDA}
\end{table}

@@

\comment{To do. DELETE???}

@@

If we lay out the circuit in 2D (hence the 2D HLF problem), it only requires classically-controlled Clifford gates\index{Clifford gates} between nearest neighbour qubits on a 2D grid. An example is shown in Fig.~\ref{fig:2DHLFgrid}. An instance of the HLF problem can be described by a graph $G(A)$ with $n$ vertices such that the off-diagonal part of A is the adjacency matrix of $G(A)$. Here $A_{i,j}=0$ unless $i,j$ are nearest neighbour vertices of the grid or $i = j$. We place qubits at each vertex and every edge corresponds to an input bit. The HLF problem is solved by applying nearest-neighbour CZ gates and $S_i$ phase gates at the correct site.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{shallow_circuits_2D}
\caption{\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid. The qubits are represented as green circles (some omitted for clarity), and CZ gates are drawn in red.}
\end{figure}

### 2018-11-16 Sections/the_quantum_sneakernet.tex
minor

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=0.7\textwidth]{sneakernet_boat}
\else
\includegraphics[clip=true, width=0.475\textwidth]{sneakernet_boat}
\fi
\caption{In the quantum Sneakernet\texttrademark entanglement distribution protocol, rather than using conventional flying qubits, we take highly error-corrected stationary qubits and physically transport them over long distances as freight. The error correction must be sufficient to maintain coherence over the time-scale of the journey, which could be anything from hours (when flying) to weeks (by sea\footnote{Or indefinitely if the destination is Australia.}). The mode of transport only transports one half of an error-corrected Bell pair, transferring the initial entanglement between source and vessel, $\ket{\Psi^+}_{A,B}$, to be between source and destination, $\ket{\Psi^+}_{A,C}$. Because all Bell pairs are identical and infinitely reproducible, latency presents no problems. For example, when using a Bell pair to teleport a qubit over long distances, when the Bell pair arrives is unimportant, as long as it's available at the time of teleportation. Thus, our Bell pair cargo carriers can simply operate in the background, transporting Bell pairs with as much bandwidth as possible, which may then be buffered by the recipient until required.}\label{fig:sneakernet_boat}	
\end{figure}

>>>>

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=0.7\textwidth]{sneakernet_boat}
\else
\includegraphics[clip=true, width=0.475\textwidth]{sneakernet_boat}
\fi
\caption{In the quantum Sneakernet\texttrademark entanglement distribution protocol, rather than using conventional flying qubits, we take highly error-corrected stationary qubits and physically transport them over long distances as freight. The error correction must be sufficient to maintain coherence over the time-scale of the journey, which could be anything from hours (when flying) to weeks (by sea\footnote{Or indefinitely if the destination is Australia and you're fleeing war crimes.}). The mode of transport only transports one half of an error-corrected Bell pair, transferring the initial entanglement between source and vessel, $\ket{\Psi^+}_{A,B}$, to be between source and destination, $\ket{\Psi^+}_{A,C}$. Because all Bell pairs are identical and infinitely reproducible, latency presents no problem. For example, when using a Bell pair to teleport a qubit over long distances, when the Bell pair arrives is unimportant, as long as it's available at the time of teleportation. Thus, our Bell pair cargo carriers can simply operate in the background, transporting Bell pairs with as much bandwidth as possible, which may then be buffered by the recipient until required, latency being unimportant provided the coherence lifetime of the error correcting code is long enough.}\label{fig:sneakernet_boat}	
\end{figure}
